Systematic Specification for Scalable Verification of Fault-Tolerant Algorithms

### 2016-10-26 doc/om-paper/paper.tex
more paper edits

\begin{definition}[Synchronous composition]
The synchronous composition of $M$ and $M'$ is a transition system
$$M | M' = (S_{M | M'}, I_{M | M'}, \rightarrow_{M | M'})$$
\noindent
such that $S_{M | M'} = S \cup S'$,
$$I_{M | M'} = \{ s_I \cup s_{I'} | s_I \in I\textnormal{, }s_{I'} \in I'\textnormal{, and } s_I \textnormal{ and } s_{I'}\textnormal{ are consistent}\}$$
\noindent
and for $s, s' \in S_{M | M'}$, $s \rightarrow_{M | M'} s'$ iff
\begin{itemize}
\item there exist states $s_M, s'_M \in S$ such that $s_M \rightarrow s'_M$, $s_M \subseteq s$, and $s'_M \subseteq s'$,
\item there exist states $s_{M'}, s'_{M'} \in S'$ such that $s_{M'} \rightarrow s'_{M'}$, $s_{M'} \subseteq s$, and $s'_{M'} \subseteq s'$,
\item $s_M$ and $s_{M'}$ are consistent,
\item and $s'_M$ and $s'_{M'}$ are consistent.
\end{itemize}
\end{definition}

@@

% ------------------------------------------------------------
\section{The Synchronous Kibitzer}\label{sec:kibitzer}
The typical approach to injecting faults into a formal model of a distributed system is to add a new state variables to each process representing its fault state. Then additional state variables are added to represent the nondeterminism introduced by faults into the state or messages by a process. Finally, additional transitions are added to each process to modify the process's state or messages based on it's current fault state.

@@

In specifying a fault-tolerant system, we must also specify a \emph{maximum fault assumption} (MFA), which specifies the maximum number of of each kind of fault that may be present in the system for some system property to hold. Define a enumeration of fault types $$\textnormal{FAULT\_TYPE} = \{none, byz, sym, man\}$$. As in the previous section, let $Id \subset \mathbb{N}$ be a finite set of indices, and let the variable $$faults: Id \rightarrow \textnormal{FAULT\_TYPE}$$ range over possible mappings from process indices to faults.

@@

>>>>

\begin{definition}[Synchronous composition]
The synchronous composition of $M$ and $M'$ is a transition system
$$M | M' = (S_{M | M'}, I_{M | M'}, \rightarrow_{M | M'})$$
\noindent
such that
\begin{itemize}
\item $S_{M | M'} = S \cup S'$,
\item $I_{M | M'} = \{ s_I \cup s_{I'} | s_I \in I\textnormal{, }s_{I'} \in I'\textnormal{, and } s_I \textnormal{ and } s_{I'}\textnormal{ are consistent}\}$
\item and for $s, s' \in S_{M | M'}$, $s \rightarrow_{M | M'} s'$ iff
  \begin{itemize}
  \item there exist states $s_M, s'_M \in S$ such that $s_M \rightarrow s'_M$, $s_M \subseteq s$, and $s'_M \subseteq s'$,
  \item there exist states $s_{M'}, s'_{M'} \in S'$ such that $s_{M'} \rightarrow s'_{M'}$, $s_{M'} \subseteq s$, and $s'_{M'} \subseteq s'$,
  \item $s_M$ and $s_{M'}$ are consistent,
  \item and $s'_M$ and $s'_{M'}$ are consistent.
  \end{itemize}
\end{itemize}
\end{definition}

@@

\subsection{The Synchronous Kibitzer}\label{sec:kibitzer}
\lee{We use synchronous composition to implement fault injection. Mention in the intro. This is fundamental to the model, so we have section devoted to it.}
The typical approach to injecting faults into a formal model of a distributed system is to add a new state variables to each process representing its fault state. Then additional state variables are added to represent the nondeterminism introduced by faults into the state or messages by a process. Finally, additional transitions are added to each process to modify the process's state or messages based on it's current fault state.

@@

In specifying a fault-tolerant system, we must also specify a \emph{maximum fault assumption} (MFA), which specifies the maximum number of of each kind of fault that may be present in the system for some system property to hold. Define a enumeration of fault types $$\textnormal{FAULT\_TYPE} = \{none, byz, sym, man\}$$ As in the previous section, let $Id \subset \mathbb{N}$ be a finite set of indices, and let the variable $$faults: Id \rightarrow \textnormal{FAULT\_TYPE}$$ range over possible mappings from process indices to faults.

@@

% ------------------------------------------------------------
